The problem and promise of scale in multilayer animal social networks

### 2020-02-14 paper/manuscript.Rmd
add placeholder lc cite

## Landscape data and habitat classification
<!-- TODO: update citation for lc product from Hance -->
Landcover data were provided by the Newfoundland and Labrador Wildlife Division.
Available landcover classification included nine habitat types at 30 m
resolution. We reclassified the landcover types into three categories: foraging
habitat, open habitat, and forest habitat using the R package `raster`
[@Hijmans_2019]. Foraging habitat consisted of lichen habitat, open habitat
consisted of wetland, rocky barrens, and anthropogenic habitat types, while
forest habitat consisted of coniferous forest, conifer scrub, broadleaf forest,
and mixed-wood forest. Water habitat was excluded from all
subsequent analyses.

>>>>

## Landscape data and habitat classification
<!-- TODO: update citation for lc product from Hance --> 
Landcover data were provided by the Newfoundland and Labrador Wildlife Division
[@Integrated_2013]. Available landcover classification included nine habitat
types at 30 m resolution. We reclassified the landcover types into three
categories: foraging habitat, open habitat, and forest habitat using the R
package `raster` [@Hijmans_2019]. Foraging habitat consisted of lichen habitat,
open habitat consisted of wetland, rocky barrens, and anthropogenic habitat
types, while forest habitat consisted of coniferous forest, conifer scrub,
broadleaf forest, and mixed-wood forest. Water habitat was excluded from all
subsequent analyses.
